paper1_results_figs_slimmed_50_rr

### 2016-06-27 inst/documents/paper1_results_figs_rr.Rmd
convert varnames from old output files

>>>>

  #27/6/16 to convert any varnames in old output files
  rownames(treeInput)[ "maleExposureProp" == rownames(treeInput) ] <- "male_exposure_prop"
  rownames(treeInput)[ "correctMixDeployProp" == rownames(treeInput) ] <- "correct_mix_deploy"
  rownames(treeInput)[ "rr_advantage_I1" == rownames(treeInput) ] <- "rr_restoration_ins1"
  rownames(treeInput)[ "rr_advantage_I2" == rownames(treeInput) ] <- "rr_restoration_ins2"

### 2016-06-27 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
convert varnames from old output files

  #input files in listOutMix, listOutIn1 & listOutI2 are the same if the runs are done with default randomSeed 
  #except that exposure will be in a.f_AB, a.f_A0 and a.f_B0 respectively (& a.m* too)
  #I could just rename one to exposure
  #BEWARE risk if future changes
  #1/2/16 don't need this now because I've saved exposure from the single original random value
  #rownames(treeInput)[rownames(treeInput)=="a.f_AB"] <- "exposure"

>>>>

  #input files in listOutMix, listOutIn1 & listOutI2 are the same if the runs are done with default randomSeed 
  #except that exposure will be in a.f_AB, a.f_A0 and a.f_B0 respectively (& a.m* too)
  #1/2/16 don't need this now because I've saved exposure from the single original random value
  #rownames(treeInput)[rownames(treeInput)=="a.f_AB"] <- "exposure"

  #27/6/16 to convert any varnames in old output files
  rownames(treeInput)[ "maleExposureProp" == rownames(treeInput) ] <- "male_exposure_prop"
  rownames(treeInput)[ "correctMixDeployProp" == rownames(treeInput) ] <- "correct_mix_deploy"
  rownames(treeInput)[ "rr_advantage_I1" == rownames(treeInput) ] <- "rr_restoration_ins1"
  rownames(treeInput)[ "rr_advantage_I2" == rownames(treeInput) ] <- "rr_restoration_ins2"
